Code Publishing Tutorial

### 2025-02-09 index.qmd
Reformat markdown
To ease change tracking in the future.
Too bad it wasn't done from the
beginning.
Address Quarto vs. rmarkdown differences

Quarto is a tool to render dynamic documents, but not the only one. You may also use [`rmarkdown`](https://rmarkdown.rstudio.com/), [Jupyter Book](https://jupyterbook.org/), [Stencila](https://stencila.io/), [Curvenote](https://curvenote.dev/), [showyourwork!](https://show-your.work/), [Org Mode](https://orgmode.org/), [StatTag](https://sites.northwestern.edu/stattag/), or one of the countless others.
:::

>>>>

Quarto is a tool to render dynamic documents, but not the only one.

It is the successor of the R package [`rmarkdown`](https://rmarkdown.rstudio.com/)
and mostly backwards-compatible.
`rmarkdown` continues to be supported,
but the development of new features happens in Quarto.
The main difference is that Quarto has first-class support for Python.
In other words, Python users of Quarto do not need to have R installed.

While this tutorial focuses on Quarto,
you can also create reproducible research projects with the following tools:

- [Jupyter Book](https://jupyterbook.org/)
- [Stencila](https://stencila.io/)
- [Curvenote](https://curvenote.dev/)
- [showyourwork!](https://show-your.work/)
- [Org Mode](https://orgmode.org/)
- [StatTag](https://sites.northwestern.edu/stattag/)
:::
